%*******************************************************
% 摘要
%*******************************************************
\clearpage
\phantomsection
\label{abstract}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}  %清除页眉横线
\pagestyle{plain}  % 去掉页眉
\setcounter{page}{1}
\pagenumbering{Roman}
%\mkheadfoot
~\vspace{-12pt}
%\titlebox{0.8}{\zhaiyaoset\titlename}
%\vspace{0.6cm}
\abstracttitle
\addcontentsline{toc}{section}{\muluzhangset 摘要}
\addcontentsline{toe}{section}{Abstract (In Chinese)}
%\pdfbookmark[1]{摘要}{abstract}
%\begin{center}
%{\zhaiyaoset 摘~~~~~~要}
%\end{center}
\zhengwenset

海洋中尺度涡旋是海洋中动能串级的重要枢纽，占据海洋~$70\%$~以上的海洋动能。关于中尺度涡旋动能来源与耗散问题，是影响海洋动力学平衡的重要问题。目前研究认为，中尺度涡旋能够与亚中尺度过程和海洋近惯性内波相互作用，是解决中尺度涡旋动能来源与耗散的潜在渠道。目前对于三者之间相互作用研究多集中于中纬度地区和南大洋，尚缺乏对北大西洋亚极地海区的系统研究。

北大西洋亚极地区域由于强烈的混合层深度变化和风暴，存在丰富的中尺度、亚中尺度过程和近惯性内波，这些过程之间有着复杂的相互作用关系，能够调节上层海洋混合、再层化以及深层对流等过程。因此，对北大西洋中尺度涡旋、亚中尺度过程以及海洋内波之间能量交换过程的研究是十分必要的，有助于提高~$\cdots\cdots$


{\guanjianciset 关键词:} 北大西洋亚极地区域；中尺度；亚中尺度~$\cdots\cdots$


\kongbaiye
%=============================================
% 英文摘要
%=============================================

\phantomsection
\pagestyle{fancy}   %激活宏包
\renewcommand{\headrulewidth}{0pt}  %清除页眉横线
\pagestyle{plain}  % 去掉页眉
%\titlebox{0.8}{\zhaiyaoset\bf\titlenameEN}
\addcontentsline{toc}{section}{Abstract}
\addcontentsline{toe}{section}{Abstract (In English)}
%\pdfbookmark[1]{Abstract}{Abstract}
\vspace{0.3cm}

\abstractENtitle
\zhengwenset

Mesoscale eddies in the ocean are an important hub of energy cascade, accounting for over $70\%$ of the oceanic kinetic energy. The issue of the energy source and dissipation of mesoscale eddies is a significant problem that affects the balance of ocean dynamics. Current studies suggest that mesoscale eddies can interact with submesoscale processes and near-inertial internal waves, providing a potential channel to address the energy source and dissipation of mesoscale eddies. However, research on the interactions among the three is mostly concentrated in mid-latitudes and the Southern Ocean, and there is a lack of systematic study on the subpolar North Atlantic region.

The subpolar North Atlantic region, with its strong variations in the depth of the mixed layer and storms, has rich mesoscale and submesoscale processes and near-inertial internal waves. These processes have complex interactions that can regulate upper ocean mixing, restratification, and deep convection. Therefore, it is essential to study the energy exchange processes among mesoscale eddies, submesoscale processes, and internal waves in the North Atlantic region to improve.

$\ldots$

{\guanjianciset \bf Key Words:} mesoscale; submesoscale; $\ldots$


%\guanjianciset {\bf{Key Words}}: compact finite difference schemes; WENO schemes; well-balanced; positivity-preserving and bound-preserving; shallow water equations and related hyperbolic conservation law

\kongbaiye


